6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-21 paper.tex
Tweaked conclusion

\usepackage{url}
\usepackage{minted}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{pdflscape}
\usepackage[style=alphabetic, sorting=nyt]{biblatex}
\addbibresource{bibliography.bib}

@@

\section{Functional Requirements}
\begin{enumerate}
  \item Testing Framework
    \begin{enumerate}
      \item The developer should be able to install the tool on their development workstation and servers.

@@

      \item The developer should be able to use to the tool to describe a system accurately and concisely.

@@

      \item The developer should be able to execute this description to validate the correctness of a system, verifying any arbitrary property as required.

@@

      \item The tool should provide an auto-detection process to detect existing services and assist in describing them.

@@

      \item The tool should provide built in checks so the developer does not have to write them all from scratch.

@@

      \item The developer should be able to use external libraries to add additional functionality to health checks.

@@

      \item The developer should be able to deploy this tool on a production server, and monitor the system continuously.

@@

      \item The tool should report results back to a central location where they can be viewed.

@@

      \item The tool should work in an environment where inbound connections to the system under test are prohibited by a firewall.

@@

    \end{enumerate}
  \item Data Collection and Monitoring
    \begin{enumerate}
      \item The tool should effectively visualise the state of a system under test, including services, components and hosts.

@@

      \item The tool should provide a way to view results of the health checks.

@@

      \item The tool should provide a way to track and visualise changes happening within the system.

@@

      \item The tool should calculate the degree of reliability of each host, service and component.

@@

      \item The tool should send Email notifications to users when incidents occur.

@@

      \item The tool should send SMS notifications to users when incidents occur.

@@

      \item The data collection and monitoring should be deployable on a private network.

@@

\section{Non-Functional Requirements}
\begin{enumerate}
  \item Reliability - The system and all of its components should provide a reliable platform for monitoring live systems.

@@

  \item Usability - It should be easy to start using the system and understand how it fits within the users existing organisation. Understanding of the implementation details should not be necessary for basic use cases.

@@

  \item Performance
    \begin{enumerate}
      \item The system should efficiently validate system correctness.

@@

      \item Alerts or warnings should be delivered in a reliable and timely fashion.

@@

      \item Validation of the system should scale above a trivial number of hosts. (Over 20)

@@

      \item The impact of validating correctness on the system under test should be minimal.\ i.e. no significant degradation in performance of the monitored applications or resource exhaustion of the hosts under test.

@@

    \end{enumerate}
  \item Security - The system is intended for use in production environments, therefore it should not unnecessarily expose the target system to threats such as the following:
    \begin{enumerate}
      \item Open network ports

@@

      \item Insecure transmission of sensitive data

@@

      \item Remote code execution

@@

    \end{enumerate}
  \item Maintainability - The system should be maintainable so that new features are easier to implement and the implementation is easier to understand for any open source contributors.

    \begin{enumerate}
      \item Separation of Concerns - The system should be decomposed into a number of separate components which can be built and tested in isolation. They may use different languages and frameworks as appropriate for the specific task.

@@

      \item Architectural Patterns - The system should make good use of appropriate design patterns and architectural techniques provided in the implementation language, such as encapsulation and composition in an object orientated language.

@@

      \item Unit Testing - Wherever possible, the code should be tested by a suite of unit tests that achieve a high coverage of the total codebase.

@@

    \end{enumerate}
  \item Interoperability - The system should integrate with existing systems in order to provide maximum flexibility/utility to the users. It should therefore:
    \begin{enumerate}
      \item Provide a simple interface such as a HTTP API to read and write data

@@

      \item Expose data in a standard format such as XML or JSON

@@

\section{Critical Evaluation}

@@

\begin{description}
  \item[Dependency on Ruby] For good reason, many of the target users of the tool are reluctant to install Ruby on production servers where it is not otherwise required. As previously discussed, the tool will manage this install process itself, reducing administrative burden, but it is still an unavoidable dependency which makes the footprint of the tool larger than necessary, and can sometimes make the installation process slow.

@@

@@

Conceptually, the main concern I have is the duplication of knowledge between actual application configuration and the test suite needed to verify it. The same could be argued for software unit testing, but it seems that with the rise in popularity of tools of a declarative nature such as Chef and Puppet, there should be a way to remove some of this duplication.

>>>>

\usepackage{url}
\usepackage{minted}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{pdflscape}
\usepackage[style=alphabetic, sorting=nyt]{biblatex}
\addbibresource{bibliography.bib}

@@

\section{Functional Requirements}
\newcommand\litem[1]{\vspace{0.2cm} \item #1 \vspace{0.2cm}}
  \begin{enumerate}
    \item Testing Framework
    \begin{enumerate}
        \litem{The developer should be able to install the tool on their development workstation and servers.}

@@

        \litem{The developer should be able to use to the tool to describe a system accurately and concisely.}

@@

      \litem{The developer should be able to execute this description to validate the correctness of a system, verifying any arbitrary property as required.}

@@

      \litem{The tool should provide an auto-detection process to detect existing services and assist in describing them.}

@@

      \litem{The tool should provide built in checks so the developer does not have to write them all from scratch.}

@@

      \litem{The developer should be able to use external libraries to add additional functionality to health checks.}

@@

      \litem{The developer should be able to deploy this tool on a production server, and monitor the system continuously.}

@@

      \litem{The tool should report results back to a central location where they can be viewed.}

@@

      \litem{The tool should work in an environment where inbound connections to the system under test are prohibited by a firewall.}

@@

    \end{enumerate}
    \item Data Collection and Monitoring
    \begin{enumerate}
      \litem{The tool should effectively visualise the state of a system under test, including services, components and hosts.}

@@

      \litem{The tool should provide a way to view results of the health checks.}

@@

      \litem{The tool should provide a way to track and visualise changes happening within the system.}

@@

      \litem{The tool should calculate the degree of reliability of each host, service and component.}

@@

      \litem{The tool should send Email notifications to users when incidents occur.}

@@

      \litem{The tool should send SMS notifications to users when incidents occur.}

@@

      \litem{The data collection and monitoring should be deployable on a private network.}

@@

\section{Non-Functional Requirements}
\begin{enumerate}
  \litem{Reliability - The system and all of its components should provide a reliable platform for monitoring live systems.}

@@

  \litem{Usability - It should be easy to start using the system and understand how it fits within the users existing organisation.} Understanding of the implementation details should not be necessary for basic use cases.

@@

    \litem{Performance}
    \begin{enumerate}
      \litem{The system should efficiently validate system correctness.}

@@

      \litem{Alerts or warnings should be delivered in a reliable and timely fashion.}

@@

      \litem{Validation of the system should scale above a trivial number of hosts. (Over 20)}

@@

      \litem{The impact of validating correctness on the system under test should be minimal.\ i.e. no significant degradation in performance of the monitored applications or resource exhaustion of the hosts under test.}

@@

    \end{enumerate}
    \litem{Security - The system is intended for use in production environments, therefore it should not unnecessarily expose the target system to threats such as the following:}
    \begin{enumerate}
        \litem{Open network ports}

@@

        \litem{Insecure transmission of sensitive data}

@@

        \litem{Remote code execution}

@@

    \end{enumerate}
    \litem{Maintainability - The system should be maintainable so that new features are easier to implement and the implementation is easier to understand for any open source contributors.}

    \begin{enumerate}
        \litem{Separation of Concerns - The system should be decomposed into a number of separate components which can be built and tested in isolation. They may use different languages and frameworks as appropriate for the specific task.}

@@

        \litem{Architectural Patterns - The system should make good use of appropriate design patterns and architectural techniques provided in the implementation language, such as encapsulation and composition in an object orientated language.}

@@

        \litem{Unit Testing - Wherever possible, the code should be tested by a suite of unit tests that achieve a high coverage of the total codebase.}

@@

    \end{enumerate}
  \litem{Interoperability - The system should integrate with existing systems in order to provide maximum flexibility/utility to the users. It should therefore:}
    \begin{enumerate}
        \litem{Provide a simple interface such as a HTTP API to read and write data}

@@

        \litem{Expose data in a standard format such as XML or JSON}

@@

\pagebreak
\section{Critical Evaluation}

@@

\begin{description}
  \item[Dependency on Ruby] For good reason, many of the target users of the tool gave feedback stating their reluctance to install Ruby on production servers where it was not otherwise required. As previously discussed, the tool will manage this install process itself, reducing administrative burden, but it is still an unavoidable dependency which makes the footprint of the tool larger than necessary, and can sometimes make the installation process slow.

@@

There are also several other clear benefits of specifying executable infrastructure models, such as the ability to generate clear architecture diagrams, effectively communicating the complexities of a system and its current state.

@@
